Msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-16 paper.tex
Systematise data/plots

\begin{figure}
\includegraphics[width=\textwidth]{figures/mutation-perf}
\caption{\label{fig-mutation-perf} Time required to run
\texttt{sim\_mutations} on tree sequences generated
by \texttt{sim\_ancestry} (with a population size of $10^4$
and recombination rate of $10^{-8}$) for varying (haploid) sample
size and sequence length. We run 10 replicate mutation simulations
each for three different mutation rates, and report the average
CPU time required (Intel Core i7-9700).
(A) Holding sequence length fixed at 10 megabases and varying the
number of samples (tree tips) from 10 to 100,000.
(B) Holding number of samples fixed at 1000, and varying the sequence
length from 1 to 100 megabases.}
\end{figure}

@@

Fig.~\ref{fig-mutation-perf} shows that the mutation generation
machinery in \msprime\ is extremely efficient, requiring
fractions of a second to generate mutations for most simulations.
For example, the longest running simulation in
Fig.~\ref{fig-mutation-perf}B required less than 2 seconds to
generate an average of 1.5 million mutations over 137,081 trees
in a tree sequence with 508,125 edges.
Generating mutations for a tree sequence is particularly efficient
because we can work edge-by-edge rather than having to
consider each tree independently.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{figures/mutations-perf}
\caption{\label{fig-mutations-perf} Time required to run
\texttt{sim\_mutations} on tree sequences generated
by \texttt{sim\_ancestry} (with a population size of $10^4$
and recombination rate of $10^{-8}$) for varying (haploid) sample
size and sequence length. We run 10 replicate mutation simulations
each for three different mutation rates, and report the average
CPU time required (Intel Core i7-9700).
(A) Holding sequence length fixed at 10 megabases and varying the
number of samples (tree tips) from 10 to 100,000.
(B) Holding number of samples fixed at 1000, and varying the sequence
length from 1 to 100 megabases.}
\end{figure}

@@

Fig.~\ref{fig-mutations-perf} shows that the mutation generation
machinery in \msprime\ is extremely efficient, requiring
fractions of a second to generate mutations for most simulations.
For example, the longest running simulation in
Fig.~\ref{fig-mutations-perf}B required less than 2 seconds to
generate an average of 1.5 million mutations over 137,081 trees
in a tree sequence with 508,125 edges.
Generating mutations for a tree sequence is particularly efficient
because we can work edge-by-edge rather than having to
consider each tree independently.
